\papertitle

### 2012-10-13 manuscript.tex
More voice-normalization commits.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit i-Bird 
RC flyer power train and clap-fling 
wings\footnote{\raggedright Silverlit Toys Manufactory Ltd.: i-Bird RC Flyer
\href{http://www.silverlit-flyingclub.com/wingsmaster/}
     {http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{ImageProc 2.4: \\
\href{https://github.com/biomimetics/imageproc\_pcb}
     {https://github.com/biomimetics/imageproc\_pcb}} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc

%----------------------------------------------------------------------------%
\subsection{Ground Station Computer Vision Platform}
% ryan
Cooperative behavior is a promising strategy for autonomous navigation of 
unexplored and unstructured environments. We intend that this system will be 
fully mobile in these environments, not tied to a static ground station or 
motion capture laboratory. To demonstrate the feasibility of this approach, 
we designed our ground station to conform to the power and weight 
constraints of highly mobile millirobotic ground vehicles, such as 
OctoRoACH, which can traverse rough terrains with speed and agility~\cite{Pullin2012Dynamic}.

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
maintain high sample rate attitude control. We estimate the vehicle pose by naively
integrating the IMU, and use a proportional plus integral plus derivative (PID) 
controller for controlling the vehicle.

The high pitch angles flapping wing flyers achieve in routine flight distinguish them 
from other MAVs. Baek demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation~\cite{baek:tracking}. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation is its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion multiplication.

@@

%----------------------------------------------------------------------------%
\subsection{Ground Station Pose Estimation}
The ground station performs simple two-dimensional pose estimation on 
H$^2$Bird using a particle filter-based motion tracking algorithm. This pose 
estimate is the feedback input to the cooperative visual servoing feedback 
loop (Sec. \ref{sec:visual_servoing_concept}). We limit our pose estimation 
approach to monocular two-dimensional object tracking in pixel space. This 
allows us to perform real-time video tracking using the modest computational 
resources available on the ground station, and similarly millirobotic ground 
vehicles.

Our pose estimation algorithm tracks H$^2$Bird motion in the frame using a 
particle filter~\cite{thrun2005probabilistic}. We initialze particles 
uniformly across the frame. To improve numerical stability, we normalize the 
weights of all particles on each iteration, and only resample the particle 
population when the mean particle weight falls below a pre-determined 
threshold.

@@

Na\"{i}ve background subtraction is brittle to changes in the scene over 
time[CITATION]. However, we found it very efficient, and reliable enough for the 
short time spans necessary for H$^2$Bird to successfully negotiate narrow 
openings, which are typically less than five seconds. Substituting $f_0$ 
with a more sophisticated extraction of the background would implement a 
more sophisticated approach to background subtraction, with no changes to 
the underlying motion tracking filter.

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
Remote guidance of the H$^2$Bird is performed by commanding relative changes in the
reference orientation. With estimates of the vehicle pose, we calculate an altitude
error and horizontal error. The ground station then commands incremental changes to 
the H$^2$Bird pitch and yaw are according to a PID control law, with positive altitude error
corresponding to negative pitch increments and positive horizontal error
corresponding to negative yaw increments. We window the controller integrator term 
to prevent windup when the bird is being launched, and tuned the derivative term
to dampen oscillations associated with the system latency [?].

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper}
% humphrey
To fulfill the need for a lightweight, autonomous flapping wing MAV platform, 
we designed the H$^2$Bird. Built around the Silverlit i-Bird 
RC flyer power train and clap-fling 
wings\footnote{\raggedright Silverlit Toys Manufactory Ltd.: i-Bird RC Flyer
\href{http://www.silverlit-flyingclub.com/wingsmaster/}
     {http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird has a wingspan of 26.5 cm and a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{ImageProc 2.4: \\
\href{https://github.com/biomimetics/imageproc\_pcb}
     {https://github.com/biomimetics/imageproc\_pcb}} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc

%----------------------------------------------------------------------------%
\subsection{Ground Station Computer Vision Platform}
% ryan
Cooperative behavior is a promising strategy for autonomous navigation of 
unexplored and unstructured environments. However, to operate in these environments,
a cooperative system must be fully mobile, not tied to a static ground station or 
motion capture laboratory. To demonstrate the feasibility of this approach, 
we designed our ground station to conform to the power and weight 
constraints of highly mobile millirobotic ground vehicles, such as 
OctoRoACH, which can traverse rough terrains with speed and agility~\cite{Pullin2012Dynamic}.

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
high sample rate attitude control. We estimate the vehicle pose by
integrating the IMU, and use a proportional plus integral plus derivative (PID) 
controller for controlling the vehicle.

The high pitch angles flapping wing flyers achieve in routine flight distinguish them 
from other MAVs. Baek demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation~\cite{baek:tracking}. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation is its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion multiplication.

@@

%----------------------------------------------------------------------------%
\subsection{Ground Station Pose Estimation}
The ground station performs simple two-dimensional pose estimation on 
H$^2$Bird using a particle filter-based motion tracking algorithm.
The produced pose estimate is the feedback input to the cooperative visual servoing feedback 
loop (Sec. \ref{sec:visual_servoing_concept}). We limit our pose estimation 
approach to monocular two-dimensional object tracking in pixel space. This 
allows us to perform real-time video tracking using the modest computational 
resources available on the ground station, and similarly, millirobotic ground 
vehicles.

Motion of the H$^2$Bird in the frame is tracked using a particle filter
with an approach similar to that employed by Thrun~\cite{thrun2005probabilistic}. 
Particles are distributed uniformly across the frame on initialization. 
To improve numerical stability, we normalize the weights of all particles on 
each iteration, and only resample the particle population when the mean particle 
weight falls below a pre-determined threshold.

@@

Na\"{i}ve background subtraction is known to be brittle to changes in the scene over 
time[CITATION]. However, we found it very efficient and sufficiently reliable for the 
short time spans necessary for H$^2$Bird to successfully negotiate narrow 
openings, which are typically less than five seconds. Substituting $f_0$ 
with a more sophisticated extraction of the background would implement a 
more sophisticated approach to background subtraction, with no changes to 
the underlying motion tracking filter.

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
The H$^2$Bird is remotely guided by commanding relative changes in its
reference orientation. Using relative changes removes the need to estimate the relative
orientation between the ground station and vehicle frames of reference. 
With estimates of the vehicle pose, we calculate an altitude
error and horizontal error. The ground station then commands incremental changes to 
the H$^2$Bird pitch and yaw are according to a PID control law, with positive altitude error
corresponding to negative pitch increments and positive horizontal error
corresponding to negative yaw increments. We window the controller integrator term 
to prevent windup when the bird is being launched, and tuned the derivative term
to dampen oscillations associated with the system latency [?].
